Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet Candidate in IC~2602

### 2020-06-02 paper/ms.tex
update transit depth constraint

\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: Validation of a Jupiter-Sized Planet in IC~2602}

@@

\begin{abstract}
We report the validation of the transiting planet TOI 837.01,
and characterization of the system using data from the NASA {\it Transiting
	Exoplanet Survey Satellite} (TESS), the ESA Gaia mission,
ground-based photometry, and spectroscopy from CTIO1.5/CHIRON,
MPG2.2/FEROS, and AAT/Veloce.
We find that TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the
``Southern Pleiades''). 
The star is therefore 40$\pm$10 million years old.
The validated planet is warm ($P = 8.YY\,{\rm d}$) and likely
Jupiter-sized. 
However, its transits are grazing: $b > 0.92$ at 3$\sigma$.
From transit photometry alone, the planetary size lies within
0.58--3.87 $R_{\rm Jup}$, due to the degeneracy
between the planetary size and its impact parameter.
From radial velocity monitoring, we find 
that its mass is less than 2.XX $M_{\rm Jup}$ (3$\sigma$).
This mass limit requires the planetary size to be below $\approx$2.X$R_{\rm Jup}$.
Non-planetary explanations for the data, most notably
hierarchical or background eclipsing binaries, are argued to be
highly unlikely on statistical grounds.
TOI 837.01 therefore tentatively joins the ranks of adolescent exoplanets orbiting
bright host stars. Further analysis of its mass, atmosphere, and obliquity could
confirm its planetary nature beyond doubt, and are worthwhile because
young planets do interesting things.
\end{abstract}

@@

For these scenarios to be viable, the flux from \tn\ and the true
eclipsing binary host would blend together, reducing the ``true''
eclipse depth $\delta_{\rm true}$ to produce the observed depth
$\delta_{\rm obs}$:
\begin{equation}
  \delta_{\rm obs}
  = 
  \delta_{\rm true} \frac{F_{\rm neighbor}}{F_{\rm total}},
\end{equation}
where the total flux and the flux from the neighbor are labelled as
such.
The requirement that the true eclipse depth is less than one
translates to a bound on the faintest possible blended companion
stars:
\begin{equation}
    \Delta m < - \frac{5}{2} \log_{10} \delta_{\rm obs}.
\end{equation}
For \tn\ ($T=9.93$), this implies that any star invoked to explain the
transit depth must be brighter than $T=15.92$.

>>>>

\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: A
Jupiter-Sized Planet Candidate in IC~2602}

@@

\begin{abstract}
We report analysis and arguments for the planetary nature of the
  transiting planet TOI 837.01.
We characterize the system using data from the NASA {\it Transiting
  Exoplanet Survey Satellite} (TESS), the ESA Gaia mission,
  ground-based photometry, and spectroscopy from CTIO1.5/CHIRON,
  MPG2.2/FEROS, and AAT/Veloce.
We find that TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the
``Southern Pleiades''). 
The star is therefore 40$\pm$10 million years old.
The validated planet is warm ($P = 8.YY\,{\rm d}$) and likely
Jupiter-sized. 
However, its transits are grazing: $b > 0.92$ at 3$\sigma$.
From transit photometry alone, the planetary size lies within
0.58--3.87 $R_{\rm Jup}$, due to the degeneracy
between the planetary size and its impact parameter.
From radial velocity monitoring, we find 
that its mass is less than 2.XX $M_{\rm Jup}$ (3$\sigma$).
This mass limit requires the planetary size to be below $\approx$2.X$R_{\rm Jup}$.
Non-planetary explanations for the data, most notably
hierarchical or background eclipsing binaries, are argued to be
highly unlikely on statistical grounds.
TOI 837.01 therefore tentatively joins the ranks of adolescent exoplanets orbiting
bright host stars. Further analysis of its mass, atmosphere, and obliquity could
confirm its planetary nature beyond doubt, and are worthwhile because
young planets do interesting things.
\end{abstract}

@@

For these scenarios to be viable, the flux from \tn\ and the true
eclipsing binary host would blend together, reducing the ``true''
eclipse depth $\delta_{\rm true}$ to produce the observed depth
$\delta_{\rm obs}$:
\begin{equation}
  \delta_{\rm obs}
  = 
  \delta_{\rm true} \frac{F_{\rm neighbor}}{F_{\rm total}},
\end{equation}
where the total flux and the flux from the neighbor are labelled as
such.
The requirement that the eclipse is produced by stars
and that $\delta_{\rm true} < 0.5$
translates to a bound on the faintest possible blended companion
stars:
\begin{equation}
    \Delta m < - \frac{5}{2} \log_{10} \left( \frac{0.5}{\delta_{\rm obs}} \right).
\end{equation}
For \tn\ ($T=9.93$), this implies that any star invoked to explain the
transit depth must be brighter than $T=15.07$.
